\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-05-26 abstract.tex
changed abstract to clarify the confusion apparent in reviews

% Sampling based falsification techniques for black box hybrid dynamical
% systems use numerical simulations to search for violations of
% properties (specified in temporal logic). This constraints them to a
% `best effort' category unlike rigorous verification techniques, which
% however require a white box model. This work tries to bridge the gap
% by presenting an automatic falsification technique which models the
% black box system before searching for a violation. It proceeds by (a)
% modeling the behavior of the system using a piecewise affine (PWA)
% discrete time model and, (b) encoding the search for a violation as a
% standard bounded model checking problem. The resulting problem is a
% disjunction of linear programs and can be solved directly using
% off-the-shelf SMT solvers or by multiple runs of a linear programming
% solver. If a counter-example is found, the existence of a
% corresponding violation in the original system is checked for
% reproducibility.

Models of embedded control systems are often so complex that they can
be treated as effectively black-box systems. Sampling-based methods
for testing such systems use numerical simulations to search for
violations of properties (specified in a suitable requirement
formalism, such as temporal logic). This constrains them to a `best
effort' category unlike rigorous verification techniques, which
however require a model amenable to symbolic analysis. This work tries
to bridge the gap by presenting an automatic falsification technique
which learns a data-driven abstraction of the black box system before
searching for a violation. It proceeds by (a) modeling the behavior of
the system using a piecewise affine (PWA) discrete-time {\em
relational} model and, (b) encoding the search for a violation in the
abstract model as a bounded model checking problem. The bounded model
checking query in this instance can be viewed as a disjunction of
conjunctions of linear constraints (i.e. linear programs) and can be
solved directly using off-the-shelf SMT solvers or by multiple runs of
a linear programming solver. For any counter-example found in the
abstraction, we check the existence of a corresponding violation in
the original system. We demonstrate the efficacy of our technique on a
few dynamical systems examples.

>>>>

Models of embedded control systems are often so complex that
falsification and testing approaches can scale only by numerically
simulating them, and hence treating the systems as black-boxes. Common
approaches like sampling-based falsification, use numerical
simulations to search for violations of safety properties. However,
this relegates them to the `best effort' category. On the other hand,
\emph{rigorous} verification (and falsification) techniques require
symbolic models and are comparatively less scalable. We try to bridge
this gap by incorporating data-driven models in a sampling based
search. Using an efficient, on-the-fly discrete abstraction
search procedure, we compute models only for selective regions of the state
space, thus `enriching' the abstraction. We then show how the
`enriched' abstraction can be used to guide the search for violations
without refinement.
%We use grid-based discrete abstractions to partition
%the state-space of the black-box hybrid dynamical system. We then use
%an efficient search procedure to find abstract violations of safety
%properties
%Assuming a grid-based implicit abstraction over the
%state-space of the black-box hybrid dynamical system, we enumerate
%abstract violations of the safety property. We then model the system
%behavior along these violations and search for concrete violations.
The automatic falsification proceeds by (a) randomly exploring the
state-space abstraction using numerically computed trajectories and
enumerating abstract violations, (b) modeling the behavior of the
system along these abstract violations by using discrete-time
piecewise affine (PWA) \emph{relational} models, and finally, (c)
encoding the search for a concrete violation as a bounded model
checking (BMC) problem.  The BMC query is then a disjunction of
conjunctions of linear constraints (i.e. combinations of linear
programs). It can be solved using off-the-shelf SMT solvers or by
multiple runs of a linear programming solver. For any counter-example
found in this `enriched' abstraction, we check the existence of a
corresponding violation in the original system. We demonstrate the
efficacy of our technique on a few benchmarks.

% Models of embedded control systems are often so complex that they can
% be treated as effectively black-box systems. Sampling-based methods
% for testing such systems use numerical simulations to search for
% violations of properties (specified in a suitable requirement
% formalism, such as temporal logic). This constrains them to a `best
% effort' category unlike rigorous verification techniques, which
% however require a model amenable to symbolic analysis. This work tries
% to bridge the gap by presenting an automatic falsification technique
% which learns a data-driven abstraction of the black box system before
% searching for a violation. It proceeds by (a) modeling the behavior of
% the system using a piecewise affine (PWA) discrete-time {\em
% relational} model and, (b) encoding the search for a violation in the
% abstract model as a bounded model checking problem. The bounded model
% checking query in this instance can be viewed as a disjunction of
% conjunctions of linear constraints (i.e. linear programs) and can be
% solved directly using off-the-shelf SMT solvers or by multiple runs of
% a linear programming solver. For any counter-example found in the
% abstraction, we check the existence of a corresponding violation in
% the original system. We demonstrate the efficacy of our technique on a
% few dynamical systems examples.

% =========================================================================
% Sampling based falsification techniques for black box hybrid dynamical
% systems use numerical simulations to search for violations of
% properties (specified in temporal logic). This constraints them to a
% `best effort' category unlike rigorous verification techniques, which
% however require a white box model. This work tries to bridge the gap
% by presenting an automatic falsification technique which models the
% black box system before searching for a violation. It proceeds by (a)
% modeling the behavior of the system using a piecewise affine (PWA)
% discrete time model and, (b) encoding the search for a violation as a
% standard bounded model checking problem. The resulting problem is a
% disjunction of linear programs and can be solved directly using
% off-the-shelf SMT solvers or by multiple runs of a linear programming
% solver. If a counter-example is found, the existence of a
% corresponding violation in the original system is checked for
% reproducibility.
